Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-05 docs/evol.tex
minor fixes - added one bibtex entry

We chose to focus our study on the security bugs rather than other
software bugs. This is because compared to other bug categories,
the category of security bugs has two distinct features: it is critical~\cite{SZ12}
and it costs~\cite{BCL08}. Specifically, a software bug can
lead to a malfunction of a software artifact that runs under specific
requirements but a security bug can allow a malicious user to alter the execution
of the entire application for his or her own gain. In this case, such bugs could span a wide
range of security and privacy issues, like viewing sensitive information, the destruction or
modification of sensitive data, denial of service and others.
Moreover, security bug disclosures lead to a negative and significant change
in market value for a software vendor~\cite{TW07}.
Hence, one of the basic pursuits in every new software release should
be the mitigation of such bugs.

@@

We explored te relation between defects with the size of a project version,
measured by the size of its {\sc jar} file by carrying out correlation tests
between the size and the defect counts for each project and its
version. The results, all statistically significant ($p \ll
0.05$) can be seen in Table~\ref{tbl:jarsizecorr}. The {\it Security
  High} category stands out by having a remarkably lower effect than
the other categories, even {\it Security Low} that nearly tops the
list.

>>>>

We chose to focus our study on the security bugs rather than other
software bugs. This is because compared to other bug categories,
the category of security bugs has two distinct features: it is critical~\cite{SZ12}
and it costs~\cite{BCL08}\cite{R06}. Specifically, a software bug can
lead to a malfunction of a software artifact that runs under specific
requirements but a security bug can allow a malicious user to alter the execution
of the entire application for his or her own gain. In this case, such bugs could span a wide
range of security and privacy issues, like viewing sensitive information, the destruction or
modification of sensitive data, denial of service and others.
Moreover, security bug disclosures lead to a negative and significant change
in market value for a software vendor~\cite{TW07}.
Hence, one of the basic pursuits in every new software release should
be the mitigation of such bugs.

@@

We explored the relation between defects with the size of a project version,
measured by the size of its {\sc jar} file by carrying out correlation tests
between the size and the defect counts for each project and its
version. The results, all statistically significant ($p \ll
0.05$) can be seen in Table~\ref{tbl:jarsizecorr}. The {\it Security
  High} category stands out by having a remarkably lower effect than
the other categories, even {\it Security Low} that nearly tops the
list.
